---
title: "Sketch people's daily schedules"
type: "lightning talk"
author: "Earo Wang"
date: ""
output:
  xaringan::moon_reader:
    css: ["default", "myremark.css"]
    self_contained: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

class: middle center

```{r initial, echo = FALSE, cache = FALSE, results = 'hide'}
library(knitr)
options(htmltools.dir.version = FALSE, tibble.width = 60)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.width = 12, fig.height = 8, fig.show = 'hold', 
  cache = TRUE, external = TRUE, dev = 'CairoPNG', dpi = 300
)
read_chunk('src/code.R')
```
```{r load}
```

```{r theme-remark}
```

```{r read}
```

## What would foot traffic look like around here on a weekday?

---

class: middle center

```{r sx4}
```

## in the bed

---

class: middle center

```{r sx5}
```

## very early bird

---

class: middle center

```{r sx6}
```

## early bird

---

class: middle center

```{r sx7}
```

## commuting to work

---

class: middle center

```{r sx8}
```

## commuting to work

---

class: middle center

```{r sx9}
```

## in the office

---

class: middle center

```{r sx10}
```

## in the office

---

class: middle center

```{r sx11}
```

## in the office

---

class: middle center

```{r sx12}
```

## lunch time

---

class: middle center

```{r sx13}
```

## lunch time

---

class: middle center

```{r sx14}
```

## in the office

---

class: middle center

```{r sx15}
```

## in the office

---

class: middle center

```{r sx16}
```

## commuting home

---

class: middle center

```{r sx17}
```

## commuting home

---

class: middle center

```{r sx18}
```

## at home

---

class: middle center

```{r sx19}
```

## in the bed
